Evolution of the AGN UV luminosity function

### 2017-09-18 Paper/paper.tex
Update text

Finally, we obtain estimates of the luminosity function.

@@

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic.pdf}
  \end{center}
  \caption{Individual luminosity function fits for $z=0.3$ to $2.6$.}
  \label{fig:mosaic}
\end{figure*}

\begin{figure*}
  \begin{center}
    \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
  \end{center}
  \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
  \label{fig:mosaic2}
\end{figure*}

>>>>

It is useful to go beyond the redshift bins of the previous section.
This gives us continuous models of luminosity function evolution and
is also relevant for extrapolation. We therefore obtain estimates of
the luminosity function.

@@

\begin{figure*}
  \begin{center}
    % \includegraphics[width=\textwidth,keepaspectratio]{mosaic_small.pdf}
    \includegraphics[height=0.9\textheight,keepaspectratio]{mosaic_small.pdf}
  \end{center}
  \caption{Individual luminosity function fits for $z=0.3$ to $2.6$.}
  \label{fig:mosaic}
\end{figure*}

%% \begin{figure*}
%%   \begin{center}
%%     \includegraphics[width=\textwidth,keepaspectratio]{mosaic2.pdf}
%%   \end{center}
%%   \caption{Individual luminosity function fits for $z=2.6$ to $6.5$.}
%%   \label{fig:mosaic2}
%% \end{figure*}
